NLTK: The Natural Language Toolkit

### 2002-05-14 technical/acl2002/acl02.tex
- Minor wording changes
svn/trunk@618

\begin{abstract}
NLTK, the Natural Language Toolkit, is a suite of open source program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learning structured
programming by example, and manipulating sophisticated models from the
outset.
\end{abstract}

@@

Teachers of introductory courses on computational linguistics are
often faced with the challenge of setting up a practical programming
component for student assignments and projects.  This is a difficult
task because different computational linguistics domains require a
variety of different data structures and functions; and because a
diverse range of topics may need to be included in the syllabus.

@@

% [EL] is ``desiderata'' an acceptable word here?
The most basic step in setting up a practical component is choosing a
suitable programming language.  A number of desiderata influenced our
choice.  First, the language must have a shallow learning curve, so
that novice programmers get immediate rewards for their efforts.
Second, the language must support rapid prototyping and a short
develop/test cycle; an obligatory compilation step is a serious
detraction.  Third, the code should be self-documenting, with a
transparent syntax and semantics.  Fourth, it should be easy to write
structured programs, ideally object-oriented but without the burden
associated with languages like C++.  Finally, the language must have
an easy-to-use graphics library to support the development of
graphical user interfaces.

>>>>

\begin{abstract}
NLTK, the Natural Language Toolkit, is a suite of open source program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learn structured
programming by example, and manipulate sophisticated models from the
outset.
\end{abstract}

@@

Teachers of introductory courses on computational linguistics are
often faced with the challenge of setting up a practical programming
component for student assignments and projects.  This is a difficult
task because different computational linguistics domains require a
variety of different data structures and functions, and because a
diverse range of topics may need to be included in the syllabus.

@@

The most basic step in setting up a practical component is choosing a
suitable programming language.  A number of considerations influenced
our choice.  First, the language must have a shallow learning curve,
so that novice programmers get immediate rewards for their efforts.
Second, the language must support rapid prototyping and a short
develop/test cycle; an obligatory compilation step is a serious
detraction.  Third, the code should be self-documenting, with a
transparent syntax and semantics.  Fourth, it should be easy to write
structured programs, ideally object-oriented but without the burden
associated with languages like C++.  Finally, the language must have
an easy-to-use graphics library to support the development of
graphical user interfaces.
